# animatrixr

`animatrixr` is a toy package I created to support a blog post I wrote on exploring animating matrix transformations using `gganimate`. It allows you to stitch together and then animate matrix transformations. For example:

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(animatrixr)

rotate_90 <- animatrixr::rotation_matrix(pi/2)

sheer_vertical <- tribble(~ x, ~ y,
                      1, 0,
                      0.5, 1) %>%
  as.matrix()

reflect_x <- tribble(~ x, ~ y,
                      1, 0,
                      0, -1) %>%
  as.matrix() 

add_transformation(m = rotate_90, seq_fun = animatrixr::seq_matrix_lp) %>% 
  add_transformation(m = sheer_vertical) %>% 
  add_transformation(m = reflect_x) %>% 
  animate_matrix(datasaurus = TRUE)
```

You can use `seq_fun` argument to specify the function used to explicitly define frames in-between the start and end of an animation of a matrix transformation.

However, this is a *toy* package. No work has gone into setting-up tests, catching errors, considering potential users, etc. Also, many visualizations you might try to make may look unintuitive (or simply come-out incorrect) -- especially involving rotations when starting outside of unit vectors.

## Installation

If you *still* want to check-it out, you can install it from from my github page:

```{r, eval = FALSE}
devtools::install_github("brshallo/animatrixr")
```
