---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# animatrixr

`animatrixr` is a *toy* package that allows you to pipe together animations of matrix transformations. For example (rotate) --> (sheer) --> (reflect) --> *ANIMATE*:

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(animatrixr)

rotate_90 <- animatrixr::rotation_matrix(pi/2)

sheer_vertical <- tribble(~ x, ~ y,
                      1, 0,
                      0.5, 1) %>%
  as.matrix()

reflect_x <- tribble(~ x, ~ y,
                      1, 0,
                      0, -1) %>%
  as.matrix() 

add_transformation(m = rotate_90, seq_fun = animatrixr::seq_matrix_lp) %>% 
  add_transformation(m = sheer_vertical) %>% 
  add_transformation(m = reflect_x) %>% 
  animate_matrix(datasaurus = TRUE)
```

You can use `seq_fun` argument to specify the function used to explicitly define frames in-between the start and end of an animation of a matrix transformation.

`animatrixr` is a *toy* package I wrote (hastily) to support a [blog post](https://www.bryanshalloway.com/2020/02/24/animatrixr-visualizing-matrix-transformations-pt-2/) on exploring animating matrix transformations using `gganimate`. The blog post doubles as providing documentation on how `animatrixr` is set-up and some of its limitations.

No work has gone into setting-up tests, catching errors, considering potential users, etc. Also, many visualizations you might try to make may look unintuitive (or simply come-out incorrect) -- especially involving rotations when starting outside of unit vectors.

## Installation

If you *still* want to check-it out, you can install it from my github page:

```{r, eval = FALSE}
devtools::install_github("brshallo/animatrixr")
```
